R functional programming approach for truncated and shifted and for shifted

### 2016-09-21 docs/shift+trunc-article/article-shift+trunc.Rmd
fevisione nomenclatura articolo

---
title: "R functional programming approach for truncated and shifted and for shifted and truncated probability distribution functions"
output: html_document
---

@@

```{r l_trunc_shift}
ltweibull <- function(x, shift = 0 ,L = -Inf, U = Inf){
  x1 <- x - shift
  # starting values for parameters (scale, shape)
  shape <- (sd(x1)/mean(x1))^(-1.086)
  scale <- mean(x1)/gamma(1+1/shape)
  # parameters vector definition
  theta <- c(shape, scale)
  # likelihood function
  ll <- function(theta, x, shift = 0, L = -Inf, U = Inf){
    shape <- theta[1]
    scale <- theta[2]
    ld <- dstweibull(x = x, shape = shape, scale = scale, shift = shift, L = L, U = U, log=TRUE)
    -sum(ld)
  }
  # maximum likelihood estimation
  optim(par = theta, fn = ll, x = x, shift=shift, L = L, U = U, method = "Nelder-Mead")[["par"]]
}
```

@@

```{r l_trunc_shift_ex}
x <- rstweibull(n = 100000, shape = 1.6, scale = 1, shift = 1, L = 1, U = 2.5)
# maximum likelihood estimate for the shifted and truncated weibull distribution
ltweibull(x = x, shift=1, L = 1, U = 2.5)
```

@@

```{r l_shift_trunc}
ltweibull <- function(x, shift = 0, L = -Inf, U = Inf){
  x1 <- x - shift
  # starting values for parameters (scale, shape)
  shape <- (sd(x1)/mean(x1))^(-1.086)
  scale <- mean(x1)/gamma(1+1/shape)
  # parameters vector definition
  theta <- c(shape, scale)
  # likelihood function
  ll <- function(theta, x, L = -Inf, U = Inf){
    shape <- theta[1]
    scale <- theta[2]
    ld <- dtsweibull(x = x, shape = shape, scale = scale, shift = shift, L = L, U = U, log=T)
    -sum(ld)
  }
  # maximum likelihood estimation
  optim(par = theta, fn = ll, x = x, L = L, U = U, method = "Nelder-Mead")[["par"]]
}
```

@@

```{r l_shift_trunc_ex}
x <- rtsweibull(n = 100000, shape = 1.6, scale = 1, shift = 1, L = 0.5, U = 3)
# maximum likelihood estimate for the shifted weibull distribution
ltweibull(x = x, shift = 1, L = 0.5, U = 3)
```

>>>>

---
title: R functional programming approach for truncated and shifted and for shifted
  and truncated probability distribution functions
output:
  html_document:
    highlight: null
    theme: null
---

@@

```{r l_trunc_shift}
lstweibull <- function(x, shift = 0 ,L = -Inf, U = Inf){
  x1 <- x - shift
  # starting values for parameters (scale, shape)
  shape <- (sd(x1)/mean(x1))^(-1.086)
  scale <- mean(x1)/gamma(1+1/shape)
  # parameters vector definition
  theta <- c(shape, scale)
  # likelihood function
  ll <- function(theta, x, shift = 0, L = -Inf, U = Inf){
    shape <- theta[1]
    scale <- theta[2]
    ld <- dstweibull(x = x, shape = shape, scale = scale, shift = shift, L = L, U = U, log=TRUE)
    -sum(ld)
  }
  # maximum likelihood estimation
  optim(par = theta, fn = ll, x = x, shift=shift, L = L, U = U, method = "Nelder-Mead")[["par"]]
}
```

@@

```{r l_trunc_shift_ex}
x <- rstweibull(n = 100000, shape = 1.6, scale = 1, shift = 1, L = 1, U = 2.5)
# maximum likelihood estimate for the shifted and truncated weibull distribution
lstweibull(x = x, shift=1, L = 1, U = 2.5)
```

@@

```{r l_shift_trunc}
ltsweibull <- function(x, shift = 0, L = -Inf, U = Inf){
  x1 <- x - shift
  # starting values for parameters (scale, shape)
  shape <- (sd(x1)/mean(x1))^(-1.086)
  scale <- mean(x1)/gamma(1+1/shape)
  # parameters vector definition
  theta <- c(shape, scale)
  # likelihood function
  ll <- function(theta, x, L = -Inf, U = Inf){
    shape <- theta[1]
    scale <- theta[2]
    ld <- dtsweibull(x = x, shape = shape, scale = scale, shift = shift, L = L, U = U, log=T)
    -sum(ld)
  }
  # maximum likelihood estimation
  optim(par = theta, fn = ll, x = x, L = L, U = U, method = "Nelder-Mead")[["par"]]
}
```

@@

```{r l_shift_trunc_ex}
x <- rtsweibull(n = 100000, shape = 1.6, scale = 1, shift = 1, L = 0.5, U = 3)
# maximum likelihood estimate for the shifted weibull distribution
ltsweibull(x = x, shift = 1, L = 0.5, U = 3)
```
